Ovarian and prostate models

### 2020-04-15 src/s_ovarian_prostate.Rmd
added prostate and ovary plots

# Prostate
```{r}
prostate <- read.csv("../data/prostate.csv", header=FALSE)

@@

mon <- monitor(fit)
saveRDS(mon, "../data/prostate_long_mon.rds")
full_data <- rstan::extract(fit, permuted=F)
r_star <- r_star_dist(full_data)
saveRDS(r_star, "../data/prostate_long_r_star.rds")
```

@@

mon <- monitor(fit)
saveRDS(mon, "../data/prostate_short_mon.rds")
full_data <- rstan::extract(fit, permuted=F)
r_star <- r_star_dist(full_data)
saveRDS(r_star, "../data/prostate_short_r_star.rds")
```

@@

g <- tibble(long=r_star_longer, short=r_star_shorter, metric="A. R*") %>% 
  bind_rows(tibble(long=mon_longer$Rhat, short=mon_shorter$Rhat, metric="B. Rhat")) %>% 
  bind_rows(tibble(long=mon_longer$Bulk_ESS, short=mon_shorter$Bulk_ESS, metric="C. Bulk ESS")) %>% 
  bind_rows(tibble(long=mon_longer$Tail_ESS, short=mon_shorter$Tail_ESS, metric="D. Tail ESS")) %>% 
  melt(id.vars="metric") %>% 
  mutate(metric=fct_relevel(as.factor(metric), "A. R*", "B. Rhat", "C. Bulk ESS", "D. Tail ESS")) %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.6) +
  facet_wrap(~metric, scales="free") +
  scale_fill_grey("MCMC info.", labels=c("4 chains: long", "16 chains: short")) +
  theme(strip.text.x = element_text(size = 10, colour="black"),
        text = element_text(size=12, colour="black"),
        axis.text = element_text(size=10, colour="black"),
        legend.text = element_text(size=12, colour="black"),
        axis.title.x = element_blank()) +
  ylab("Count")
ggsave("../output/prostate.pdf", g, width = 12, height = 8)
```

>>>>

# Prostate

```{r}
prostate <- read.csv("../data/prostate.csv", header=FALSE)

@@

mon <- monitor(fit)
saveRDS(mon, "../data/prostate_long_mon.rds")
full_data <- rstan::extract(fit, permuted=F)

# Thin data again
r_star <- r_star_dist(full_data[, , seq(1, 18106, 5)])
saveRDS(r_star, "../data/prostate_long_r_star.rds")
```

@@

mon <- monitor(fit)
saveRDS(mon, "../data/prostate_short_mon.rds")
full_data <- rstan::extract(fit, permuted=F)
r_star <- r_star_dist(full_data[, , seq(1, 18106, 5)])
saveRDS(r_star, "../data/prostate_short_r_star.rds")
```

@@

my_breaks <- function(x) { if (max(x) < 10) c(0.95, max(x)) else c(0, max(x)) }

g <- tibble(long=r_star_longer, short=r_star_shorter, metric="A. R*") %>% 
  bind_rows(tibble(long=mon_longer$Rhat, short=mon_shorter$Rhat, metric="B. Rhat")) %>% 
  bind_rows(tibble(long=mon_longer$Bulk_ESS, short=mon_shorter$Bulk_ESS, metric="C. Bulk ESS")) %>% 
  bind_rows(tibble(long=mon_longer$Tail_ESS, short=mon_shorter$Tail_ESS, metric="D. Tail ESS")) %>% 
  melt(id.vars="metric") %>% 
  mutate(metric=fct_relevel(as.factor(metric), "A. R*", "B. Rhat", "C. Bulk ESS", "D. Tail ESS")) %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.6) +
  facet_wrap(~metric, scales="free") +
  scale_fill_grey("MCMC info.", labels=c("4 chains: long", "16 chains: short")) +
  theme(strip.text.x = element_text(size = 10, colour="black"),
        text = element_text(size=12, colour="black"),
        axis.text = element_text(size=10, colour="black"),
        legend.text = element_text(size=12, colour="black"),
        axis.title.x = element_blank()) +
  ylab("Count") +
  scale_x_continuous(limits=my_breaks)
ggsave("../output/prostate.pdf", g, width = 12, height = 8)
```
